A formal approach but practical approach in train regulation

### 2025-06-12 paper/main.tex
grammaire train/régulateur

Now, we come to the train model. Each train has an identifier. In other words, we have a set of trains $\trains = \{1, \ldots, k\}$. Each train has a position on the network. The position is the index of the block it stays in or the last block it was in. Next, a train has a direction in $\directions$. The direction does not mean the train is running---it can be blocked by some red signal---but that its next move will be in that direction. Finally, a train has duties. Duties are given as a sequence of orders following the grammar:
$$  seq ::= \su(dir,pos) $$
with $dir \in \directions$ and $pos \in \blocks$. A duty $\su(dir, pos)$ states that the train direction is set to $dir$ and that the train runs until it reaches $pos$.  The sequence may be empty.

>>>>

Now, we come to the train model. Each train has an identifier. In other words, we have a set of trains $\trains = \{1, \ldots, k\}$. Each train has a position on the network. The position is the index of the block it stays in or the last block it was in. Next, a train has a direction in $\directions$. The direction does not mean the train is running---it can be blocked by some red signal---but that its next move will be in that direction. Finally, a train has duties. Duties are given as a sequence of orders following the grammar:
$$  seq ::= \su(dir,pos) $$

%Je pose ça ici, si ça peut vous aider
\begin{grammar}[Trains' grammar][h][trains_grammar]
    \firstcasesubtil{T}{\concat{seq}{T}}{}
    \otherform{\varepsilon }{}
    \firstcasesubtil{seq}{StartUntil(D,N)}{}
    \firstcasesubtil{D}{f \gralt b}{}
    \firstcasesubtil{N}{[ sections ]}{}
    \firstcasesubtil{sections}{\concat{section}{sections} \gralt section \gralt \varepsilon}{} 
    \firstcasesubtil{section}{0 \gralt 1 \gralt ... }{} 
\end{grammar}

with $dir \in \directions$ and $pos \in \blocks$. A duty $\su(dir, pos)$ states that the train direction is set to $dir$ and that the train runs until it reaches $pos$.  The sequence may be empty. 
\\
%idem pour le régulateur
About the regulator, here is the grammar we use to describe its orders:
\begin{grammar}[Regulator's grammar][h][regulateur]
    \firstcasesubtil{R}{stmt || R}{}
    \otherform{\varepsilon}{}
    \firstcasesubtil{stmt}{ev(id_{train}, num_{event}) : atom}{}
    \firstcasesubtil{atom}{incr(j)}{}
    \otherform{att(j, value_{j})}{}
    \otherform{turn(id_{switch}, state)}{}
    \otherform{auth}{}
    \otherform{atom \gralt \varepsilon}{}
\end{grammar}
